---
format: dashboard
title: ""
theme:
  - darkly
  - stravawattz.scss
expandable: false
---

```{r script-preparation}
suppressPackageStartupMessages({
  
  library(dplyr)
  library(jsonlite)
  library(httr)
  library(ggplot2)
  library(stringr)
  library(tidyr)
  library(purrr)
  library(lubridate)
  library(leaflet)
  library(DT)
  library(plotly)
  library(openmeteo)
  library(RColorBrewer)
  library(clipr)
  library(scales)
  library(reshape2)
  
})
load("stravawattz.RData")
```

# 2025

## Row {height="100%"}

### Column {width="14%"}

#### Row {height="20%"}

```{r running-box-sessions-2025}
#| content: valuebox
list(
  title = paste("Running Sessions"),
  #icon = "hash",
  color = "success",
  value = paste0(length((df_all_distinct %>% filter(type == "Run" & year(date) == 2025))$id), " sessions")
)
```

#### Row {height="20%"}

```{r running-box-distance-2025}
#| content: valuebox
#| title: "Total Distance"
list(
  color = "success",
  value = paste0(round(sum((df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% select(distance)), na.rm = TRUE) / 1000, 0), " km")
)
```

#### Row {height="20%"}

```{r running-box-time-2025}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  color = "success",
  value = ifelse(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 / 60), 0),"h ", ifelse(round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(time), na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="20%"}

```{r running-box-elevation-2025}
#| content: valuebox
#| title: "Total Elevation"
list(
  color = "success",
  value = ifelse(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(elevation), na.rm = TRUE) < 1000, paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(elevation), na.rm = TRUE), 1), " m"), paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(elevation), na.rm = TRUE)/1000, 1), " km"))
)
```

#### Row {height="20%"}

```{r running-box-cadence-2025}
#| content: valuebox
#| title: "Average Cadence"
list(
  color = "success",
  value = ifelse(is.nan(avg_cad <- with(df_all_distinct %>% filter(type == "Run", year(date) == 2025), mean(cadence, na.rm = TRUE))), "No data", paste0(round(avg_cad), " bpm"))
)
```

#### Row {height="20%"}

```{r running-box-pace-2025}
#| content: valuebox
#| title: "Average Pace"
list(
  color = "success",
  value = ifelse(is.nan(as.numeric(floor(pace <- mean((df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(pace)), na.rm = TRUE)), ":", round((pace %% 1) * 60))), "No data", paste0(floor(pace <- mean((df_all_distinct %>% filter(type == "Run" & year(date) == 2025) %>% pull(pace)), na.rm = TRUE)), ":", ifelse(round((pace %% 1) * 60) < 10, paste0("0", round((pace %% 1) * 60)), round((pace %% 1) * 60)), "/km"))
)
```

#### Row {height="20%"}

```{r running-box-hr-2025}
#| content: valuebox
#| title: "Average HR"
list(
  color = "success",
  value = ifelse(is.nan(avg_hr <- with(df_all_distinct %>% filter(type == "Run", year(date) == 2025), sum(speed * hr, na.rm = TRUE) / sum(speed, na.rm = TRUE))), "No data", paste0(round(avg_hr), " bpm"))
)
```

### Column {width="43%"}

#### Row {height="25%"}

##### Column {.tabset title="Calendar"}

```{r running-daily-calendar-2025}
#| padding: 0px
#| title: "Daily"
plot_calendar_daily_run_2025
```

```{r running-weekly-calendar-2025}
#| padding: 0px
#| title: "Weekly"
plot_calendar_weekly_run_2025
```

```{r running-monthly-calendar-2025}
#| padding: 0px
#| title: "Monthly"
plot_calendar_monthly_run_2025
```

#### Row {height="75%"}

##### Column {.tabset title="Rankings"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_run_2025
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_run_2025
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_elevation_run_2025
```

```{r}
#| padding: 0px
#| title: "Pace"
plot_pace_run_2025
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_run_2025
```

```{r}
#| padding: 0px
#| title: "TRIMP"
plot_trimp_run_2025
```

### Column {width="43%"}

#### Row {height="25%"}

##### Column {.tabset title="Cumulative"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_cumul_distance_run_2025
```

```{r}
#| padding: 0px
#| title: "Time"
plot_cumul_time_run_2025
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_cumul_elevation_run_2025
```

#### Row {height="75%"}

##### Column {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map_sep_last_run_2025
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map_sep_fast_run_2025
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map_sep_long_run_2025
```

```{r}
#| title: "All"
#| padding: 0px 
plot_map_heat_run_2025
```

# 2024

## Row {height="100%"}

### Column {width="14%"}

#### Row {height="20%"}

```{r running-box-sessions-2024}
#| content: valuebox
list(
  title = paste("Running Sessions"),
  #icon = "hash",
  color = "success",
  value = paste0(length((df_all_distinct %>% filter(type == "Run" & year(date) == 2024))$id), " sessions")
)
```

#### Row {height="20%"}

```{r running-box-distance-2024}
#| content: valuebox
#| title: "Total Distance"
list(
  color = "success",
  value = paste0(round(sum((df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% select(distance)), na.rm = TRUE) / 1000, 0), " km")
)
```

#### Row {height="20%"}

```{r running-box-time-2024}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  color = "success",
  value = ifelse(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 / 60), 0),"h ", ifelse(round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(time), na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="20%"}

```{r running-box-elevation-2024}
#| content: valuebox
#| title: "Total Elevation"
list(
  color = "success",
  value = ifelse(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(elevation), na.rm = TRUE) < 1000, paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(elevation), na.rm = TRUE), 1), " m"), paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(elevation), na.rm = TRUE)/1000, 1), " km"))
)
```

#### Row {height="20%"}

```{r running-box-cadence-2024}
#| content: valuebox
#| title: "Average Cadence"
list(
  color = "success",
  value = ifelse(is.nan(avg_cad <- with(df_all_distinct %>% filter(type == "Run", year(date) == 2024), mean(cadence, na.rm = TRUE))), "No data", paste0(round(avg_cad), " bpm"))
)
```

#### Row {height="20%"}

```{r running-box-pace-2024}
#| content: valuebox
#| title: "Average Pace"
list(
  color = "success",
  value = ifelse(is.nan(as.numeric(floor(pace <- mean((df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(pace)), na.rm = TRUE)), ":", round((pace %% 1) * 60))), "No data", paste0(floor(pace <- mean((df_all_distinct %>% filter(type == "Run" & year(date) == 2024) %>% pull(pace)), na.rm = TRUE)), ":", ifelse(round((pace %% 1) * 60) < 10, paste0("0", round((pace %% 1) * 60)), round((pace %% 1) * 60)), "/km"))
)
```

#### Row {height="20%"}

```{r running-box-hr-2024}
#| content: valuebox
#| title: "Average HR"
list(
  color = "success",
  value = ifelse(is.nan(avg_hr <- with(df_all_distinct %>% filter(type == "Run", year(date) == 2024), sum(speed * hr, na.rm = TRUE) / sum(speed, na.rm = TRUE))), "No data", paste0(round(avg_hr), " bpm"))
)
```

### Column {width="43%"}

#### Row {height="25%"}

##### Column {.tabset title="Calendar"}

```{r running-daily-calendar-2024}
#| padding: 0px
#| title: "Daily"
plot_calendar_daily_run_2024
```

```{r running-weekly-calendar-2024}
#| padding: 0px
#| title: "Weekly"
plot_calendar_weekly_run_2024
```

```{r running-monthly-calendar-2024}
#| padding: 0px
#| title: "Monthly"
plot_calendar_monthly_run_2024
```

#### Row {height="75%"}

##### Column {.tabset title="Rankings"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_run_2024
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_run_2024
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_elevation_run_2024
```

```{r}
#| padding: 0px
#| title: "Pace"
plot_pace_run_2024
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_run_2024
```

```{r}
#| padding: 0px
#| title: "TRIMP"
plot_trimp_run_2024
```

### Column {width="43%"}

#### Row {height="25%"}

##### Column {.tabset title="Cumulative"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_cumul_distance_run_2024
```

```{r}
#| padding: 0px
#| title: "Time"
plot_cumul_time_run_2024
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_cumul_elevation_run_2024
```

#### Row {height="75%"}

##### Column {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map_sep_last_run_2024
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map_sep_fast_run_2024
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map_sep_long_run_2024
```

```{r}
#| title: "All"
#| padding: 0px 
plot_map_heat_run_2024
```

# 2023

## Row {height="100%"}

### Column {width="14%"}

#### Row {height="20%"}

```{r running-box-sessions-2023}
#| content: valuebox
list(
  title = paste("Running Sessions"),
  #icon = "hash",
  color = "success",
  value = paste0(length((df_all_distinct %>% filter(type == "Run" & year(date) == 2023))$id), " sessions")
)
```

#### Row {height="20%"}

```{r running-box-distance-2023}
#| content: valuebox
#| title: "Total Distance"
list(
  color = "success",
  value = paste0(round(sum((df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% select(distance)), na.rm = TRUE) / 1000, 0), " km")
)
```

#### Row {height="20%"}

```{r running-box-time-2023}
#| content: valuebox
#| title: "Total Duration"
#| padding: 0px
list(
  color = "success",
  value = ifelse(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 >= 300, paste0(round(floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 / 60), 0),"h ", ifelse(round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)<10,paste0("0",round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)),round(((sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 / 60) - floor(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60 / 60)) * 60, 0)), "min"), paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(time), na.rm = TRUE) / 60, 0), "min"))
)
```

#### Row {height="20%"}

```{r running-box-elevation-2023}
#| content: valuebox
#| title: "Total Elevation"
list(
  color = "success",
  value = ifelse(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(elevation), na.rm = TRUE) < 1000, paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(elevation), na.rm = TRUE), 1), " m"), paste0(round(sum(df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(elevation), na.rm = TRUE)/1000, 1), " km"))
)
```

#### Row {height="20%"}

```{r running-box-cadence-2023}
#| content: valuebox
#| title: "Average Cadence"
list(
  color = "success",
  value = ifelse(is.nan(avg_cad <- with(df_all_distinct %>% filter(type == "Run", year(date) == 2023), mean(cadence, na.rm = TRUE))), "No data", paste0(round(avg_cad), " bpm"))
)
```

#### Row {height="20%"}

```{r running-box-pace-2023}
#| content: valuebox
#| title: "Average Pace"
list(
  color = "success",
  value = ifelse(is.nan(as.numeric(floor(pace <- mean((df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(pace)), na.rm = TRUE)), ":", round((pace %% 1) * 60))), "No data", paste0(floor(pace <- mean((df_all_distinct %>% filter(type == "Run" & year(date) == 2023) %>% pull(pace)), na.rm = TRUE)), ":", ifelse(round((pace %% 1) * 60) < 10, paste0("0", round((pace %% 1) * 60)), round((pace %% 1) * 60)), "/km"))
)
```

#### Row {height="20%"}

```{r running-box-hr-2023}
#| content: valuebox
#| title: "Average HR"
list(
  color = "success",
  value = ifelse(is.nan(avg_hr <- with(df_all_distinct %>% filter(type == "Run", year(date) == 2023), sum(speed * hr, na.rm = TRUE) / sum(speed, na.rm = TRUE))), "No data", paste0(round(avg_hr), " bpm"))
)
```

### Column {width="43%"}

#### Row {height="25%"}

##### Column {.tabset title="Calendar"}

```{r running-daily-calendar-2023}
#| padding: 0px
#| title: "Daily"
plot_calendar_daily_run_2023
```

```{r running-weekly-calendar-2023}
#| padding: 0px
#| title: "Weekly"
plot_calendar_weekly_run_2023
```

```{r running-monthly-calendar-2023}
#| padding: 0px
#| title: "Monthly"
plot_calendar_monthly_run_2023
```

#### Row {height="75%"}

##### Column {.tabset title="Rankings"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_distance_run_2023
```

```{r}
#| padding: 0px
#| title: "Time"
plot_time_run_2023
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_elevation_run_2023
```

```{r}
#| padding: 0px
#| title: "Pace"
plot_pace_run_2023
```

```{r}
#| padding: 0px
#| title: "HR"
plot_hr_run_2023
```

```{r}
#| padding: 0px
#| title: "TRIMP"
plot_trimp_run_2023
```

### Column {width="43%"}

#### Row {height="25%"}

##### Column {.tabset title="Cumulative"}

```{r}
#| padding: 0px
#| title: "Distance"
plot_cumul_distance_run_2023
```

```{r}
#| padding: 0px
#| title: "Time"
plot_cumul_time_run_2023
```

```{r}
#| padding: 0px
#| title: "Elevation"
plot_cumul_elevation_run_2023
```

#### Row {height="75%"}

##### Column {.tabset title="Maps"}

```{r}
#| title: "Latest"
#| padding: 0px 
plot_map_sep_last_run_2023
```

```{r}
#| title: "Fastest"
#| padding: 0px 
plot_map_sep_fast_run_2023
```

```{r}
#| title: "Longest"
#| padding: 0px 
plot_map_sep_long_run_2023
```

```{r}
#| title: "All"
#| padding: 0px 
plot_map_heat_run_2023
```
