---
format: dashboard
title: ""
theme:
  - darkly
  - stravawattz.scss
expandable: false
---

```{r script-preparation}
suppressPackageStartupMessages({
  
  library(dplyr)
  library(jsonlite)
  library(httr)
  library(ggplot2)
  library(stringr)
  library(tidyr)
  library(purrr)
  library(lubridate)
  library(leaflet)
  library(DT)
  library(plotly)
  library(openmeteo)
  library(RColorBrewer)
  library(clipr)
  library(scales)
  library(reshape2)
  
})
load("stravawattz.RData")
```

# 2025

## Row {height="100%"}

### Column {width="50%"}

#### Row {height="25%"}

##### Column

```{r training-load-gauge-atl-2025}
plot_gauge_tload_ATL_2025
```

##### Column

```{r training-load-gauge-ctl-2025}
plot_gauge_tload_CTL_2025
```

##### Column

```{r training-load-gauge-acwr-2025}
plot_gauge_tload_ACWR_2025
```

#### Row {height="75%"}

##### Column {.tabset title="Current load metrics"}

```{r training-load-all-2025}
#| padding: 0px
#| title: "All metrics"
plot_training_load_2025
```

### Column {width="50%"}

#### Row {height="25%"}

##### Column

```{r tloa-box1-2025}
#| content: valuebox
#| title: "Current Status"
list(
  color = "dark",
  value = status_today
)
```

##### Column

```{r tloa-box2-2025}
#| content: valuebox
#| title: "Suggested Recovery"
list(
  color = "dark",
  value = paste0(suggest_training_plan_2025$suggested_rest_days, " days")
)
```

##### Column

```{r tloa-box3-2025}
#| content: valuebox
#| title: "Suggested Training"
list(
  color = "dark",
  value = suggest_training_plan_2025$suggested_training_type
)
```

#### Row {height="75%"}

##### Column {.tabset title="Expected ACWR after workout"}

```{r acwr-expected-t0-2025}
#| padding: 0px
#| title: "Today"
plot_acwr_projection_0_2025
```

```{r acwr-expected-t1-2025}
#| padding: 0px
#| title: "T+1"
plot_acwr_projection_1_2025
```

```{r acwr-expected-t2-2025}
#| padding: 0px
#| title: "T+2"
plot_acwr_projection_2_2025
```

```{r acwr-expected-t3-2025}
#| padding: 0px
#| title: "T+3"
plot_acwr_projection_3_2025
```

# 2024

## Row {height="100%"}

### Column {width="50%"}

#### Row {height="25%"}

##### Column

```{r training-load-gauge-atl-2024}
plot_gauge_tload_ATL_2024
```

##### Column

```{r training-load-gauge-ctl-2024}
plot_gauge_tload_CTL_2024
```

##### Column

```{r training-load-gauge-acwr-2024}
plot_gauge_tload_ACWR_2024
```

#### Row {height="75%"}

##### Column {.tabset title="Current load metrics"}

```{r training-load-all-2024}
#| padding: 0px
#| title: "All metrics"
plot_training_load_2024
```

### Column {width="50%"}

#### Row {height="25%"}

##### Column

```{r tloa-box1-2024}
#| content: valuebox
#| title: "Current Status"
list(
  color = "dark",
  value = status_today
)
```

##### Column

```{r tloa-box2-2024}
#| content: valuebox
#| title: "Suggested Recovery"
list(
  color = "dark",
  value = paste0(suggest_training_plan_2024$suggested_rest_days, " days")
)
```

##### Column

```{r tloa-box3-2024}
#| content: valuebox
#| title: "Suggested Training"
list(
  color = "dark",
  value = suggest_training_plan_2024$suggested_training_type
)
```

#### Row {height="75%"}

##### Column {.tabset title="Expected ACWR after workout"}

```{r acwr-expected-t0-2024}
#| padding: 0px
#| title: "Today"
plot_acwr_projection_0_2024
```

```{r acwr-expected-t1-2024}
#| padding: 0px
#| title: "T+1"
plot_acwr_projection_1_2024
```

```{r acwr-expected-t2-2024}
#| padding: 0px
#| title: "T+2"
plot_acwr_projection_2_2024
```

```{r acwr-expected-t3-2024}
#| padding: 0px
#| title: "T+3"
plot_acwr_projection_3_2024
```

# 2023

## Row {height="100%"}

### Column {width="50%"}

#### Row {height="25%"}

##### Column

```{r training-load-gauge-atl-2023}
plot_gauge_tload_ATL_2023
```

##### Column

```{r training-load-gauge-ctl-2023}
plot_gauge_tload_CTL_2023
```

##### Column

```{r training-load-gauge-acwr-2023}
plot_gauge_tload_ACWR_2023
```

#### Row {height="75%"}

##### Column {.tabset title="Current load metrics"}

```{r training-load-all-2023}
#| padding: 0px
#| title: "All metrics"
plot_training_load_2023
```

### Column {width="50%"}

#### Row {height="25%"}

##### Column

```{r tloa-box1-2023}
#| content: valuebox
#| title: "Current Status"
list(
  color = "dark",
  value = status_today
)
```

##### Column

```{r tloa-box2-2023}
#| content: valuebox
#| title: "Suggested Recovery"
list(
  color = "dark",
  value = paste0(suggest_training_plan_2023$suggested_rest_days, " days")
)
```

##### Column

```{r tloa-box3-2023}
#| content: valuebox
#| title: "Suggested Training"
list(
  color = "dark",
  value = suggest_training_plan_2023$suggested_training_type
)
```

#### Row {height="75%"}

##### Column {.tabset title="Expected ACWR after workout"}

```{r acwr-expected-t0-2023}
#| padding: 0px
#| title: "Today"
plot_acwr_projection_0_2023
```

```{r acwr-expected-t1-2023}
#| padding: 0px
#| title: "T+1"
plot_acwr_projection_1_2023
```

```{r acwr-expected-t2-2023}
#| padding: 0px
#| title: "T+2"
plot_acwr_projection_2_2023
```

```{r acwr-expected-t3-2023}
#| padding: 0px
#| title: "T+3"
plot_acwr_projection_3_2023
```
